A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2023-01-09 kobakian-cook.Rmd
small changes to code

## Prepare to plot
fort_hex <- fortify_hexagon(data = aus_hexmap,
                            sf_id = "sa2_name_2011",
                            hex_size = 0.2) %>% 
            left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))
fort_aus <- sa2thyroid_ERP %>%
  fortify_sfc()
## Make a plot
aus_hexmap_plot <- ggplot() +
  geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
  scale_fill_identity() +
  invthm + coord_equal()
```

@@

```{r dorl}
# Non - Contiguous Dorling Cartograms
dorl <- sa2thyroid_ERP %>% 
  filter(!is.na(Population)) %>% 
  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
  cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
d <- st_bbox(dorl)
tas_ggdorl <- ggplot(dorl) +
  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) + 
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() +
  guides(fill = "none") +
  theme_map() #+ ggtitle("c")
#tas_ggdorl
```

```{r tasdisplays, out.width="100%", fig.width = 8, fig.height = 3, layout = "l-body", fig.cap = "The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania. The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility. The Dorling expands the metropolitan regions."}
#library(gridExtra)
cowplot::plot_grid(tas_ggcont, 
                   tas_ggncont, 
                   tas_ggdorl, ncol=3,
                   labels = c("a", "b", "c"))
```

>>>>

## Prepare to plot
fort_hex <- fortify_hexagon(data = aus_hexmap,
                            sf_id = "sa2_name_2011",
                            hex_size = 0.2) %>% 
            left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))
fort_aus <- sa2thyroid_ERP %>%
  fortify_sfc()
## Make a plot
aus_hexmap_plot <- ggplot() +
  geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
               fill = "black",  colour = "darkgrey",  linewidth = 0.1, data = fort_aus) +
  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
  scale_fill_identity() +
  invthm + coord_equal()
```

@@

```{r dorl}
# Non - Contiguous Dorling Cartograms
if (!file.exists("data/dorl.rda")) {
  dorl <- sa2thyroid_ERP %>% 
    filter(!is.na(Population)) %>% 
  # mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
    cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
  save(dorl, file = "data/dorl.rda")
}

load("data/dorl.rda")
d <- st_bbox(dorl)
tas_ggdorl <- ggplot(dorl) +
  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) + 
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() +
  guides(fill = "none") +
  theme_map() #+ ggtitle("c")
```

```{r tasdisplays, out.width="100%", fig.width = 8, fig.height = 3, layout = "l-body", fig.cap = "The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania. The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility. The Dorling expands the metropolitan regions."}
cowplot::plot_grid(tas_ggcont, 
                   tas_ggncont, 
                   tas_ggdorl, ncol=3,
                   labels = c("a", "b", "c"))
```
